Fourmile Calibrations and Output

### 2024-10-04 fourmile_outputs_2013edits.Rmd
added hru climate outputs and hru rd/rg

@@

@@

@@

rh

@@

>>>>

############################
### look at month
#get rid of a bunch of data
hru_grid_tmean_jan <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean_jan <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus_jan <- left_join(hru_grid_tmean_jan, hru_statn_tmean_jan, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean_jan <- left_join(hrus, tmean_hrus_jan, by = 'value')

tmean_jan <- ggplot() +
  geom_sf(data = hrus_map_tmean_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

#tmean_jan

## 
hru_grid_tmean_apr <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean_apr <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus_apr <- left_join(hru_grid_tmean_apr, hru_statn_tmean_apr, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean_apr <- left_join(hrus, tmean_hrus_apr, by = 'value')

tmean_apr <- ggplot() +
  geom_sf(data = hrus_map_tmean_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

#tmean_apr

#### 
hru_grid_tmean_jul <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean_jul <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus_jul <- left_join(hru_grid_tmean_jul, hru_statn_tmean_jul, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean_jul <- left_join(hrus, tmean_hrus_jul, by = 'value')

tmean_jul <- ggplot() +
  geom_sf(data = hrus_map_tmean_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
                            limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

#tmean_jul

##

hru_grid_tmean_sep <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean_sep <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus_sep <- left_join(hru_grid_tmean_sep, hru_statn_tmean_sep, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean_sep <- left_join(hrus, tmean_hrus_sep, by = 'value')

tmean_sep <- ggplot() +
  geom_sf(data = hrus_map_tmean_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

#tmean_sep
###

lots <- ggarrange(tmean_jan,
                  tmean_apr,
                  tmean_jul,
                  tmean_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

#################
# winter p
hru_grid_precip <- hru_grids %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_grid = precip)

precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(1,2,3)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip_jan <- left_join(hrus, precip_hrus_jan, by = 'value')

precip_jan <- ggplot() +
  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

##
precip_hrus_apr <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip_apr <- left_join(hrus, precip_hrus_apr, by = 'value')

precip_apr <- ggplot() +
  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')
##

precip_hrus_jul <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip_jul <- left_join(hrus, precip_hrus_jul, by = 'value')

precip_jul <- ggplot() +
  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

## 
precip_hrus_sep <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip_sep <- left_join(hrus, precip_hrus_sep, by = 'value')

precip_sep <- ggplot() +
  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
                       limits = c(-51, 7.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

lots <- ggarrange(precip_jan,
                  precip_apr,
                  precip_jul,
                  precip_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

##########
### look at month
#get rid of a bunch of data
hru_grid_solrad_jan <- hru_grids %>%
  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad_jan <- hru_statn %>%
  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus_jan <- left_join(hru_grid_solrad_jan, hru_statn_solrad_jan, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad_jan <- left_join(hrus, solrad_hrus_jan, by = 'value')

solrad_jan <- ggplot() +
  geom_sf(data = hrus_map_solrad_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
                       limits = c(-8.5, 1.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

#solrad_jan

## 
hru_grid_solrad_apr <- hru_grids %>%
  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad_apr <- hru_statn %>%
  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus_apr <- left_join(hru_grid_solrad_apr, hru_statn_solrad_apr, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad_apr <- left_join(hrus, solrad_hrus_apr, by = 'value')

solrad_apr <- ggplot() +
  geom_sf(data = hrus_map_solrad_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
                       limits = c(-8.5, 1.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

#solrad_apr

#### 
hru_grid_solrad_jul <- hru_grids %>%
  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad_jul <- hru_statn %>%
  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus_jul <- left_join(hru_grid_solrad_jul, hru_statn_solrad_jul, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad_jul <- left_join(hrus, solrad_hrus_jul, by = 'value')

solrad_jul <- ggplot() +
  geom_sf(data = hrus_map_solrad_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
                       limits = c(-8.5, 1.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

#solrad_jul

##
hru_grid_solrad_sep <- hru_grids %>%
  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad_sep <- hru_statn %>%
  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus_sep <- left_join(hru_grid_solrad_sep, hru_statn_solrad_sep, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad_sep <- left_join(hrus, solrad_hrus_sep, by = 'value')

solrad_sep <- ggplot() +
  geom_sf(data = hrus_map_solrad_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
                       limits = c(-8.5, 1.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

###

lots <- ggarrange(solrad_jan,
                  solrad_apr,
                  solrad_jul,
                  solrad_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

rh
#####

hru_grid_rh_jan <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_jan <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus_jan <- left_join(hru_grid_rh_jan, hru_statn_rh_jan, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh_jan <- left_join(hrus, rh_hrus_jan, by = 'value')

rh_jan <- ggplot() +
  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

##
hru_grid_rh_apr <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_apr <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus_apr <- left_join(hru_grid_rh_apr, hru_statn_rh_apr, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh_apr <- left_join(hrus, rh_hrus_apr, by = 'value')

rh_apr <- ggplot() +
  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

##
hru_grid_rh_jul <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_jul <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus_jul <- left_join(hru_grid_rh_jul, hru_statn_rh_jul, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh_jul <- left_join(hrus, rh_hrus_jul, by = 'value')

rh_jul <- ggplot() +
  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

##
hru_grid_rh_sep <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,10)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_sep <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,10)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus_sep <- left_join(hru_grid_rh_sep, hru_statn_rh_sep, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh_sep <- left_join(hrus, rh_hrus_sep, by = 'value')

rh_sep <- ggplot() +
  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

lots <- ggarrange(rh_jan,
                  rh_apr,
                  rh_jul,
                  rh_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

# HRU RD/RG

Group 1 is lowest elevation, 4 is highest elevation

setwd("~/Documents/Repos/fourmile")

elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv') %>%
  mutate(elevation_group = ntile(elevation, 4))

rd1_grid <- hru_grids %>%
  dplyr::select(time, outRD1, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rd1_summed = cumsum(outRD1)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rd1_summed = max(rd1_summed)) %>%
  mutate(type = 'grid')

rd1_statn <- hru_statn %>%
  dplyr::select(time, outRD1, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rd1_summed = cumsum(outRD1)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rd1_summed = max(rd1_summed)) %>%
  mutate(type = 'statn')

rd1_hru <- bind_rows(rd1_grid, rd1_statn)

# elevation group area
elev_area <- elev %>%
  group_by(elevation_group) %>%
  summarize(group_area = sum(area))

rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
  mutate(RD1_mm_year = (max_rd1_summed/group_area)*1000)

library(viridis)

rd1_plot <- ggplot(rd1_hru, aes(x=as.factor(year), y=RD1_mm_year, 
                                      color=as.factor(elevation_group),
                                      shape = type)) + 
  geom_point(size = 3) +
  #scale_color_viridis_d() +
  theme_bw() +
  labs(x = 'Year',
       y = 'Total RD1 (mm/year)')

ggplotly(rd1_plot)

###########################

rd2_grid <- hru_grids %>%
  dplyr::select(time, outRD2, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rd2_summed = cumsum(outRD2)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rd2_summed = max(rd2_summed)) %>%
  mutate(type = 'grid')

rd2_statn <- hru_statn %>%
  dplyr::select(time, outRD2, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rd2_summed = cumsum(outRD2)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rd2_summed = max(rd2_summed)) %>%
  mutate(type = 'statn')

rd2_hru <- bind_rows(rd2_grid, rd2_statn)

rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rd2_mm_year = (max_rd2_summed/group_area)*1000)

rd2_plot <- ggplot(rd2_hru, aes(x=as.factor(year), y=rd2_mm_year, 
                                      color=as.factor(elevation_group),
                                      shape = type)) + 
  geom_point(size = 3) +
  #scale_color_viridis_d() +
  theme_bw() +
  labs(x = 'Year',
       y = 'Total RD2 (mm/year)')

ggplotly(rd2_plot)

###########

# RG1
rg1_grid <- hru_grids %>%
  dplyr::select(time, outRG1, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rg1_summed = cumsum(outRG1)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rg1_summed = max(rg1_summed)) %>%
  mutate(type = 'grid')

rg1_statn <- hru_statn %>%
  dplyr::select(time, outRG1, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rg1_summed = cumsum(outRG1)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rg1_summed = max(rg1_summed)) %>%
  mutate(type = 'statn')

rg1_hru <- bind_rows(rg1_grid, rg1_statn)

rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg1_mm_year = (max_rg1_summed/group_area)*1000)

rg1_plot <- ggplot(rg1_hru, aes(x=as.factor(year), y=rg1_mm_year, 
                                      color=as.factor(elevation_group),
                                      shape = type)) + 
  geom_point(size = 3) +
  #scale_color_viridis_d() +
  theme_bw() +
  labs(x = 'Year',
       y = 'Total RG1 (mm/year)')

ggplotly(rg1_plot)

#######

# rg2
rg2_grid <- hru_grids %>%
  dplyr::select(time, outRG2, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rg2_summed = cumsum(outRG2)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rg2_summed = max(rg2_summed)) %>%
  mutate(type = 'grid')

rg2_statn <- hru_statn %>%
  dplyr::select(time, outRG2, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  group_by(year, elevation_group) %>%
  mutate(rg2_summed = cumsum(outRG2)) %>%
  group_by(year, elevation_group) %>%
  summarise(max_rg2_summed = max(rg2_summed)) %>%
  mutate(type = 'statn')

rg2_hru <- bind_rows(rg2_grid, rg2_statn)

rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg2_mm_year = (max_rg2_summed/group_area)*1000)

rg2_plot <- ggplot(rg2_hru, aes(x=as.factor(year), y=rg2_mm_year, 
                                      color=as.factor(elevation_group),
                                      shape = type)) + 
  geom_point(size = 3) +
  #scale_color_viridis_d() +
  theme_bw() +
  labs(x = 'Year',
       y = 'Total RG2 (mm/year)')

ggplotly(rg2_plot)
